---
output:
  github_document:
    html_preview: true
---

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```
```{r, echo=FALSE, results='asis'}
bcgovr::insert_bcgov_devex_badge("Exploration")
```
[![License](https://img.shields.io/badge/License-Apache%202.0-blue.svg)](https://opensource.org/licenses/Apache-2.0)

# CC_Biodiversity_Refugia
This repository presents 2 analysis; 1) generates a macro refugia layering using BEC 1970 and BEC 2080 identifying equivalent areas; and 2) Intactness classifying human area and linear disturbance, ranking them according to their severity. A third Enduring Features is in development.

### Data
For the macro refugia analysis  current and 2080 modelled BEC were used - from: Wang, Tongli, Elizabeth M. Campbell, Gregory A. O’Neill, and Sally N. Aitken. 2012. “Projecting Future Distributions of Ecosystem Climate Niches: Uncertainties and Management Applications.” Forest Ecology and Management 279 (September): 128–40. https://doi.org/10.1016/j.foreco.2012.05.034. (https://cfcg.forestry.ubc.ca/projects/climate-data/climatebcwna/)

For Intactness the analysis uses the Skeena East Environmental Stewardship Initiative (ESI) Area as a case-study. Previoulsy compiled Forest Age, Logging Year, Human Footprint, railroads, pipelines, hydro transmission corridors and road type where used. Methods are available on request.

### Usage

There are 3 sets core scripts that are required for analysis, each set (macroRefugia, Footprint, EnduringFeatures) needs to be run in order:

- 01_load.R
- 01_load_macroRefugia.R
- 01_load_Footprint.R
- 01_load_EnduringFeatures.R
- 02_clean_macroRefugia.R
- 02_clean_Footprint.R
- 02_clean_EnduringFeatures.R
- 03_analysis_BECoverlap.R
- 03_analysis_Footprint.R
- 04_output_macroRefugia.R

### Project Status
This project is part of Climate Change and Biodiversity assessment being led by the Ministry of Environment and Climate Change Strategy's Ecosystem Branch. The analysis is exploratory and will be added to and updated over the coming months. 

### Getting Help or Reporting an Issues

To report bugs/issues/feature requests, please file an [issue](https://github.com/bcgov/CC_Biodiversity_Refugia/issues/).

### How to Contribute

If you would like to contribute, please see our [CONTRIBUTING](CONTRIBUTING.md) guidelines.

Please note that this project is released with a [Contributor Code of Conduct](CODE_OF_CONDUCT.md). By participating in this project you agree to abide by its terms.

### License

```
Copyright 2020 Province of British Columbia

Licensed under the Apache License, Version 2.0 (the &quot;License&quot;);
you may not use this file except in compliance with the License.
You may obtain a copy of the License at

http://www.apache.org/licenses/LICENSE-2.0

Unless required by applicable law or agreed to in writing, software distributed under the License is distributed on an &quot;AS IS&quot; BASIS,
WITHOUT WARRANTIES OR CONDITIONS OF ANY KIND, either express or implied.
See the License for the specific language governing permissions and limitations under the License.
```

This repository is maintained by [ENVEcosystems](https://github.com/orgs/bcgov/teams/envecosystems/members). 
